%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 1.0 (10/6/2012)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important:
% This template needs to be compiled using XeLaTeX
%
% Note: this template has the option to use the Hoefler Text font, see the
% font configurations section below for instructions on using this font
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{article} % Document font size and paper size

\usepackage{fontspec} % Allows the use of OpenType fonts

\usepackage{geometry} % Allows the configuration of document margins
\geometry{a4paper, textwidth=5.5in, textheight=10in, marginparsep=7pt, marginparwidth=.6in} % Document margin settings %%% textheight was = 8.5
\setlength\parindent{0in} % Remove paragraph indentation

\usepackage[usenames,dvipsnames]{xcolor} % Custom colors

\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage[normalem]{ulem} % Custom underlining
\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text} % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\scriptsize \raise .3ex\hbox{#1}}} % New command for including margin years %%%I added the \raise and \hbox commands to make the vertical alignment better
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt} % Slightly increase the distance of the margin years from the content
\reversemarginpar

\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Jordan Creed - CV},pdfauthor={Jordan Creed}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} % Link colors

\usepackage{textpos} %%%for positioning text box in the upper right corner

\usepackage{enumitem} %%%for adjusting indent in enumerate environment

\usepackage{longtable}

%----------------------------------------------------------------------------------------
%	FONT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% Two font choices are available in this template, the default is Linux Libertine, available for free at: http://www.linuxlibertine.org while the secondary choice is Hoefler Text which comes bundled with Mac OSX.
% To use Hoefler Text, comment out the Linux Libertine block below and uncomment the Hoefler Text block. You will also need to replace the "\&" characters with "\amper{}" in section titles.

% Hoefler Text Font (bundled with Mac OSX)
\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
\setsansfont[Scale=0.9]{Optima Regular} % Set sans font, used in the main name and titles in the document
\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}} % Custom ampersand character
%\sectionfont{\sffamily\mdseries\large\underline} % Set font options for sections
\sectionfont{\rmfamily\mdseries\scshape\normalsize\underline} % Set font options for sections as subsections %%%
\subsectionfont{\rmfamily\mdseries\scshape\normalsize} % Set font options for subsections
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} % Set font options for subsubsections

%----------------------------------------------------------------------------------------

\begin{document}

\begin{textblock*}{3.5cm}(10.1cm,-1cm)
  {\footnotesize Curriculum Vitae\\Prepared \today}
\end{textblock*}

%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

{\Large Jordan Creed}\\[.5cm] % was LARGE and [1cm]
Informatics Application Developer, Department of Health Informatics\\[.2cm]
Moffitt Cancer Center\\
12902 Magnolia Drive\\ 
%Mailstop: MRC-CANCONT\\
Tampa, FL 33612\\[.2cm] 
Phone: 813-833-0887\\ 
Email: \href{mailto:Jordan.H.Creed@moffitt.org}{Jordan.H.Creed@moffitt.org}\\[.2cm]
%\textsc{url}: \href{http://www.travisgerke.com}{http://www.travisgerke.com}\\


%------------------------------------------------
\vspace{-.3cm}

\section*{Education}
\years{2015} B.H.S.~(Public Health), University of Florida, Gainesville, FL\\
\years{2016} M.P.H.~(Biostatistics), University of Florida, Gainesville, FL
%\years{2017--} Non-degree~(Statistics), University of South Florida, Tampa, FL

\section*{Academic appointments and employment}
\years{2013-2014}Undergraduate Intern, Maru Diagnostic Imaging Services, Tampa, FL\\
\years{2014}Undergraduate Intern, The Kyle Practice, Belfast, Northern Ireland, UK\\
\years{2016}Graduate Intern, Department of Biostatistics, H.\ Lee Moffitt Cancer Center \& Research Institute, Tampa, FL\\
\years{2016--2018}Research Data Analyst I (Bioinformatics), Department of Cancer Epidemiology, H.\ Lee Moffitt Cancer Center \& Research Institute, Tampa, FL\\
\years{2018--2021}Research Data Analyst II (Bioinformatics), Department of Cancer Epidemiology, H.\ Lee Moffitt Cancer Center \& Research Institute, Tampa, FL\\
\years{2020--}Graduate Research Assistant, College of Public Health, University of South Florida, Tampa, FL\\
\years{2021--}Informatics Application Developer, Department of Health Informatics, H.\ Lee Moffitt Cancer Center \& Research Institute, Tampa, FL\\

\section*{Teaching}
\years{2021--}Instructor, BSC6939: Introduction to R Programming, University of South Florida

%\section*{Training}

%\section*{Honors and awards}

%\section*{Research support}

%\section*{Dissertation}

\section*{Service}
\emph{Moffitt Cancer Center}
~\\
\years{2017}Member, Bioinformatics Interest Meeting\\
\years{2018--2020}Member, Bio-Data Club\\
\years{2019--}Member, Hackathon Organizing Committee\\
\years{2020--}Co-Organizer, Bio-Data Club\\

\emph{University of Florida}
~\\
\years{2013--2015}Member, Health Occupations Students of America\\
\years{2014--2015}Member, Health Science Students Organization\\
\years{2014--2016}Secretary, Public Health Students Association\\

\emph{Professional}\\
%~\\
\years{2017--2018}Co-Organizer, Tampa Bay R Users Group, Tampa, FL\\
\years{2018--}Organizer, Tampa Bay R Users Group, Tampa, FL \\
\years{2018--}Affiliate Member, American Association of Cancer Research (AACR) \\
\years{2019--}Member, R-Ladies Tampa, Tampa, FL\\ 
\years{2020--} Ad hoc reviewer, American Medical Informatics Association Annual Symposium (x4) \\
%\years{2018}Speaker, Great American Teach In, Tampa, FL \\
%\years{2018}R Meetup Chair, Data Analysis Using R Workshop, Tampa, FL \\

%\section*{Professional association memberships}
%\years{2011--}Active member, Transdisciplinary Prostate Cancer Partnership (ToPCaP), Boston, MA\\

\section*{Peer-reviewed publications}
\begin{enumerate}[leftmargin=*]

\item{} Miller B, Peeri NC, Nabors LB, {\bf CreedJH}, Thompson ZJ, Rozmeski CM, LaRocca RV, Chowdhary S, Olson JJ, Thompson RC, Egan KM. Handedness and the risk of glioma. J
Neurooncol. 2018 May;137(3):639-644. doi: 10.1007/s11060-018-2759-y. Epub 2018
Jan 13. PubMed PMID: 29332185; PubMed Central PMCID: PMC5924459.

\item{} Peeri NC*, {\bf Creed JH*}, Anic GM, Thompson RC, Olson JJ, LaRocca RV, Chowdhary SA, Brockman JD, Gerke TA, Nabors LB, Egan KM (*co-first authors). Toenail selenium, genetic variation in selenoproteins and risk and outcome in glioma. Cancer Epidemiology 2018; DOI:10.1016/j.canep.2018.02.002

\item{} {\bf Creed JH}, Aden-Buie G, Monteiro AN, Gerke TA. epiTAD: a web application for visualizing  chromosome conformation capture data in the context of genetic epidemiology. Bioinformatics 2019; DOI: 10.1093/bioinformatics/btz387

\item{} {\bf Creed JH*}, Peeri NC*, Anic GM, Thompson RC, Olson JJ, LaRocca RV, Chowdhary SA, Brockman JD, Gerke TA, Nabors LB, Egan KM (*co-first authors). Methylmercury exposure, genetic variation in metabolic enzymes, and the risk of glioma. Sci Rep 2019; DOI: 10.1038/s41598-019-47284-4

\item{} {\bf Creed JH}, Berglund AE, Rounbehler RJ, Awasthi S, Cleveland JL, Park JY, Yamoah K, Gerke TA. Commercial gene expression tests for prostate cancer prognosis provide paradoxical estimates of race-specific risk. Cancer Epidemiol Biomarkers Prev 2019; DOI: 10.1158/1055-9965.EPI-19-0407

\item{} {\bf Creed JH}, Gerke TA, Berglund AE. MatSurv: Survival analysis and visualization in MATLAB. Journal of Open Source Software 2020, 5(46), 1830; DOI: 10.21105/joss.01830

\item{} {\bf Creed JH}, Smith-Warner SA, Gerke TA, Egan KM. A prospective study of coffee and tea consumption and the risk of glioma in the UK Biobank. Eur J Cancer 2020; DOI: 10.1016/j.ejca.2020.01.012

\item{} Hernandez-Prera J, Valderrabano P, {\bf Creed J}, Iglesia J, Slebo R, Centeno BA, Tarasova V, Hallanger-Johnson J, Veloski C, Otto KJ, Wenig BM, Yoder S, Lam C, Park DS, Anderson AR, Raghunand N, Berglund A, Caudell J, Gerke TA, Chung CH.  Molecular determinants of thyroid nodules with indeterminate cytology and RAS mutations. Thyroid 2020; DOI: 10.1089/thy.2019.0650

\item{} Cote DJ, Smith-Warner SA, {\bf Creed JH}, Furtado J, Gerke TA, Wang M, Kim Y, Stampfer MJ, Egan KM. Circulating lipids and glioma risk: results from the UK Biobank, Nurses’ Health Study, and Health Professionals Follow-Up Study. Cancer Causes \& Control 2021; DOI: 10.1007/s10552-021-01391-8

\item{} Yue Y, {\bf Creed JH}, Cote DJ, Stampfer MJ, Wang M, Midttun O, McCann A, Ueland PM, Furtado J, Egan KM, Smith-Warner SA. Pre-diagnostic circulating concentrations of fat-soluble vitamins and risk of glioma in three cohort studies. SciRep 2021; DOI: 10.1038/s41598-021-88485-0

\item{} Samanic CM, Cote DJ, {\bf Creed JH}, Stampfer MJ, Wang M, Smith-Warner SA, Egan KM. Prospective study of sleep duration and glioma risk. Cancer Causes Control; DOI: 10.1007/s10552-021-01447-9

\item{} Cote DJ, {\bf Creed JH}, Samanic CM, Gerke TA, Stampfer MJ, Smith-Warner SA, Egan KM. A prospective study of inflammatory biomarkers and growth factors and risk of glioma in the UK Biobank. Cancer Epidemiology 2021; DOI: 10.1016/j.canep.2021.102043

\end{enumerate}

\section*{Preprints}
\begin{enumerate}[leftmargin=*]

\item{} {\bf Creed JH}, Monteiro AN, Gerke TA. epiTAD: a web application for visualizing high throughput chromosome conformation capture data in the context of genetic epidemiology. bioRxiv 243840. \href{https://www.biorxiv.org/content/early/2018/01/05/243840}{https://www.biorxiv.org/content/early/2018/01/05/243840}

\item{} {\bf Creed JH}, Berglund AE, Rounbehler RJ, Awasthi S, Cleveland JL, Park JY, Gerke TA. Commercial gene expression tests for prostate cancer prognosis provide  paradoxical estimates of race-specific risk. bioRvix 604058. \\\href{https://www.biorxiv.org/content/10.1101/604058v1.full}{https://www.biorxiv.org/content/10.1101/604058v1.full}

\item{} Wilson C, Thapa R, {\bf Creed JH} Nguyen J, Segura CM, Gerke TA, Schildkraut J, Peres L, Fridley BL. Statistical framework for studying the spatial architecture of the tumor immune microenvironment., 
\end{enumerate}

\section*{Manuscripts In Prep}
\begin{enumerate}[leftmargin=*]

\item{} {\bf Creed JH}, Nwogu O, Gerke TA. Distribution of effect estimates and p-values estimated from the top medical literature, 2000-2010. 

\end{enumerate}

\section*{Book Chapters}
\begin{enumerate}[leftmargin=*]

\item{} Berglund AE, Putney RM, {\bf Creed JH}, Aden-Buie G, Gerke TA, Rounbehler RJ. Accessible pipeline for translational research using TCGA: Examples of relating gene mechanism to disease specific outcomes. In: Markowitz J. (eds) Translational Bioinformatics for Therapeutic Development. Methods in Molecular Biology, vol 2194. Humana, New York, NY, 2021. \href{https://doi.org/10.1007/978-1-0716-0849-4_8}{https://doi.org/10.1007/978-1-0716-0849-4\_8} \\

\end{enumerate}

\section*{Conference presentations}
\vspace{-.3cm}
{\footnotesize\emph{$*$ denotes oral presentation, -- denotes poster presentation}}\\

-- {\bf Creed JH}, Chi YY, Chen DT. Interactive analysis of cancer genomics and clinical outcomes for the NanoString nCounter platform. In: Public Health Day: 2016 August; Gainesville, FL.\\

-- {\bf Creed JH}, Gerke T, Monteiro A. EpiTAD Viewer: A Software Application for Visualizing and Contextualizing HI-C Data in Genetic Epidemiology. In: Moffitt Scientific Symposium: 2017 May 4; Tampa, FL. Award: {\bf Population Science Poster Winner.}\\

-- Gerke T, Tyekucheva S, {\bf Creed JH}, Penney KL, Sinnott JA, Ebot E, Berglund AE, Loda M, Stampfer MJ, Kraft P, Parmigiani G, Mucci LA. All happy families are alike: Transcriptomic homogeneity in indolent prostate tumors is a useful prognostic biomarker. In: Prostate Cancer: Advances in Basic, Translational, and Clinical Research (AACR Special Conference): 2017 Dec 2--5; Orlando, FL. \\

-- {\bf Creed JH}, Berglund AE, Yamoah KJ, Gerke TA. Ancestry informative eQTLs in prostate tumor tissue: implications for observed cancer disparities. In: USF Health Research Day: 2018 Feb 23; Tampa, FL. \\

-- Nwogu O, {\bf Creed JH}, Egan KM, Gerke TA. Leveraging eQTL Analysis to Identify Genes Associated with Glioblastoma Multiforme Survival. In: USF Health Research Day: 2018 Feb 23; Tampa, FL. \\

-- Berglund A, Putney R, {\bf Creed J}, Aden-Buie G, Gerke T, Rounbehler R. Accessible pipeline for translational research using TCGA: Tristetraprolin as an example relating gene mechanism to disease specific outcomes. In: TCGA Legacy: Multi-Omic Studies in Cancer: 2018 Sep 27--29; Washington, DC.\\

-- Laajala TD, Aden-Buie G, Gerke T, {\bf Creed J}, Berglund A, Stopsack K, Cramer SD, Tyekucheva S, Aittokallio T, Costello JC. Identifying genetic interactions that drive aggressive prostate cancer using an ensemble of penalized Cox regression models.  In: AACR Convergence: Artificial Intelligence, Big Data, and Prediction in Cancer: 2018 Oct 14--17; Newport, RI. \\

-- {\bf Creed JH}, Awasthi S, Yamoah KJ, Gerke TA. Gleason grade progresses in a race-dependent manner. In: 43rd Annual Society of Preventive Oncology Conference: 2019 Mar 10--12; Tampa, FL. \\

-- Awasthi S, {\bf Creed JH}, Williams V, Gerke TA, Yamoah K. Treatment related race disparities in long term survival among very low risk prostate cancer patients. In: 43rd Annual Society of Preventive Oncology Conference: 2019 Mar 10--12; Tampa, FL. \\

$*$ {\bf Creed JH}, Berglund AE, Rounbehler RJ, Awasthi S, Cleveland JL, Park JY, Gerke TA. Commercial gene expression tests for prostate cancer prognosis provide  paradoxical estimates of race-specific risk. In: AACR Annual Meeting - Factors influencing cancer outcomes minisymposium: 2019 March 29--April 3; Atlanta, GA. \\

-- Awasthi S, {\bf Creed JH}, Asamoah F, Williams VL, Fink AK, Dhillon J, Park J, Gerke TA, Yamoah K. Rethinking early intervention for healthy young men with very low risk prostate cancer; does race matter? In: Moffitt Scientific Symposium: 2019 May 2; Tampa, FL. \\

-- Aden-Buie G, {\bf Creed JH}, Gerke TA. A web application and software package for analysis and exploration of the FCDS Florida Cancer Registry Data. In: Moffitt Scientific Symposium: 2019 May 2; Tampa, FL. \\

$*$ {\bf Creed JH}, Gerke TA. Global ancestry estimation and data repository for the TCGA pan-cancer resource.  In: Moffitt Scientific Symposium: 2019 May 2; Tampa, FL. \\

-- Carvajal R, Gonzalez-Calderon G, Betin-Montes M, Gai-Cherry R, {\bf Creed JH}, Gerke TA, Eschrich S, Berglund A. Patient Timelines for Research-Oriented Exploration of Longitudinal Cancer Patient Data: PT Explorer. In: American Medical Informatics Association (AMIA) 2019 Annual Symposium: 2019 Nov 16--20; Washington, DC. Award: {\bf Distinguished Poster.}\\

$*$ {\bf Creed JH}, Gerke, TA. mediator: an R package for causal mediation analysis.  In: 2020 Statistical Practice in Cancer Conference: 2020 February 28; Tampa, FL. \\ 

$*$ {\bf Creed JH}, Shahla B, Aden-Buie G, Yamoah K, Gerke, TA. A framework to reduce analytic complexity for longitudinal data.  In: 2020 Moffitt Scientific Symposium: 2020 May 20; Tampa, FL. \\ 

-- Samanic C, Teer JK, Thompson ZJ, {\bf Creed JH}, Nabros LB, Williams SL, Egan KM. Mitochondrial DNA Sequence Variation and Risk of Glioma. In: 2020 Society for Neuro-Oncology Annual Meeting. 

\section*{Certification}

\years{2020} Tidyverse Instructor Certification 

\section*{Conferences and Workshops}

\years{2018} Frontiers in Statistics: Data Science across Disciplines. University of South Florida, Tampa, FL. Health Science Chair. \\
\years{2018} Data Analysis Using R. University of South Florida, Tampa, FL. R Meetup Chair \\ 
\years{2019} Intermediate Shiny Workshop. rstudio::conf January 15--16;  Austin, TX.  \\
\years{2019} Integrative Molecular Epidemiology: Bridging Cancer Biology and Percision Medicine. AACR July 14 --19; Boston, MA. \\
\years{2020} Building Tidy Tools Workshop. rstudio::conf January 27--28; San Francisco, CA.  \\
\years{2020} Rstudio Instructor Workshop. RStudio November 2--3; Tampa, FL (virtual Rstudio-led training). \\

\section*{Presentations and Talks}

\years{2018} Introduction to Shiny. In: R Meetup Tampa: 2018 March 29; Tampa, FL.\\
\years{2018} Introduction to R. In: Data Analysis Using R: 2018 November 5; Tampa, FL. \\
\years{2018} Improving reproducible research with shiny. In: Data Analysis Using R: 2018 November 9; Tampa, FL. \\
\years{2019} Visualizing genomic data with karyoploteR. In: BioData Club: 2019 June 21; Tampa, FL.\\ 
\years{2019} Navigating Maps in R. In: R Ladies Tampa: 2019 September 14; Tampa, FL.\\ 
\years{2020} Creating R packages. In: BioData Club: 2020 July 17; Tampa, FL. \\

%\years{2018} Introduction to shiny. In: R Meetup Tampa: 2018 March 29; Tampa, FL.

%\section*{Invited seminars}
%\years{2009}A method for resolving ties in asymptotic relative efficiency. Undergraduate Research Symposium, University of Florida.\\

\section*{Software development}

{\bf Creed JH}, Aden-Buie G, Monteiro AN, Gerke TA. \verb|epiTAD|: A web application for visualizing high throughput chromosome conformation capture data in the context of genetic epidemiology, \href{https://apps.gerkelab.com/epiTAD/}{https://apps.gerkelab.com/epiTAD/}. R Shiny Application 2018; latest development version \href{https://github.com/GerkeLab/epiTAD}{https://github.com/GerkeLab/epiTAD}.\\

{\bf Creed JH}, Gerke TA, Berglund AE. \verb|MatSurv|: Survival analysis and visualization in MatLab. MatLab package 2019; latest development version \href{https://github.com/aebergl/MatSurv}{https://github.com/aebergl/MatSurv}. \\ 

{\bf Creed JH}, Aden-Buie G, Gerke TA. \verb|ShinyDAG|: A web application for building, analyzing, and visualizing directed acyclic graphs (DAGs), \href{https://apps.gerkelab.com/shinyDAG/}{https://apps.gerkelab.com/shinyDAG/}. R Shiny Application 2018; latest development version \href{https://github.com/GerkeLab/ShinyDAG}{https://github.com/GerkeLab/ShinyDAG}. \\

{\bf Creed JH}, Aden-Buie G, Gerke TA. \verb|mediator|: An R package for implementing causal mediation analyses. R package 2019; latest development version \href{https://github.com/GerkeLab/mediator}{https://github.com/GerkeLab/mediator}. \\

{\bf Creed JH}, Thapa R, Wilson C, Fridley B. \verb|spatialTIME|: Spatial Analysis of Vectra Immunoflourescent Data. R package 2021; latest development version
\\\href{https://github.com/FridleyLab/spatialTIME}{https://github.com/FridleyLab/spatialTIME}. \\


\section*{Support}

\begin{longtable}{@{}p{0.2\linewidth} p{0.75\linewidth}}
Date: & 10/08/2019 \\
Funding Source: &  R Consortium \\
Title: & Bad Idea Hackathon 2019 \\
Role: & Organizer \\
Amount: & \$200 \\
\end{longtable}

\section*{Awards}

\years{2018} rstudio::conf Diversity Scholarship \\
\years{2020--} USF College of Public Health Doctoral Fellowship \\

%Barr CD, {\bf Gerke TA}, Diez DM. \verb|voronoi|: Methods and applications related to Voronoi tessellations. R package 2011; version 1.0.

\section*{Other education}

Principles of Molecular Medicine : 2017 Aug 21 - Dec 4; Department of Medical Sciences, University of South Florida, Tampa, FL\\

Applied Bioinformatics : 2017 Aug 22 - Dec 5; Department of Medical Sciences, University of South Florida, Tampa, Fl \\

Genome Data Analysis Course:  2017 Sept 20 - Nov 15; Department of Bioinformatics, Moffitt Cancer Center, Tampa, FL \\

Special Topics in Statistics :  2018 Jan 17 -  May 2; Department of Mathematics and Statistics, University of South Florida, Tampa, FL

Snowflake Fundamentals : 2021 May 12 - 13; Tampa, FL (virtual training) 

%------------------------------------------------

%\vfill{} % Whitespace before final footer
%----------------------------------------------------------------------------------------
%	FINAL FOOTER
%----------------------------------------------------------------------------------------
%\begin{center}
%{\scriptsize Last updated: \today\- \- \href{http://www.LaTeXTemplates.com}{http://www.LaTeXTemplates.com}} % Any final footer text such as a URL to the latest version of your CV, last updated date, compiled in XeTeX, etc
%\end{center}
%----------------------------------------------------------------------------------------

\end{document}